Deep mutational scanning of hemagglutinin helps distinguish the evolutionary fate of human H3N2 influenza virus lineages

### 2018-01-15 paper/manuscript.tex
updated Significance Statement

% Please add here a significance statement to explain the relevance of your work
% 120 words max
\significancestatement{
Mutations drive the rapid evolution of seasonal influenza virus such that new strains emerge and co-circulate until one strain overtakes the population. 
A key challenge in the study of seasonal influenza virus is to be able to differentiate between strains that are likely to persist and those that are likely to die out. 
We therefore need a greater understanding of how mutations drive and constrain viral evolution in order to help identify persistent and nonpersistent strains. 
We experimentally measured the effect of every possible amino-acid mutation to the surface protein hemagglutinin on viral growth.
Using these measurements, we revealed differences between successful and unsuccessful viral lineages and examined how generalizable the measurements were for studying the evolutionary fate of viral lineages.
\comment{Our work has potential for use in forecasting}
}

>>>>

% Please add here a significance statement to explain the relevance of your work
% 120 words max
\significancestatement{ 
A key goal in the study of influenza virus evolution is to forecast which viral strains will persist and which ones will die out. 
Here we experimentally measure the effects of all amino-acid mutations to the hemagglutinin protein from a human H3N2 influenza strain on viral growth in cell culture.
We show that these measurements have utility for distinguishing among viral strains that do and do not succeed in nature.
Overall, our work suggest that new high-throughput experimental approaches may be useful for evolutionary forecasting.
}
